Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-28 ms.tex
clean up

\begin{deluxetable}{llllll}
\label{tab:model_comparison}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
\end{deluxetable}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the FIXME GCM. Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
\label{fig:spectra}
\end{figure*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM. We also show the planet-to-star flux corresponding to each map (points). The planet-to-star flux is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} temperature maps from the best fit models and the GCM at 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

\begin{deluxetable*}{llllllllllll}
\tablecolumns{12}
\tablewidth{0pt}:
\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
\tablehead{
\colhead{$\lambda$} & \colhead{Dilution} & \colhead{0.1} & \colhead{0.2} & \colhead{0.3} & \colhead{0.4} & \colhead{0.6} & \colhead{0.7} & \colhead{0.8} & \colhead{0.9} & \colhead{X} & \colhead{Y}}
\startdata
1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ -15 \pm 66 $ & $ 142 \pm 67 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 120 \pm 64 $ & $ 42 \pm 65 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 139 \pm 64 $ & $ -8 \pm 65 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 4 \pm 63 $ & $ 144 \pm 64 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 131 \pm 67 $ & $ 52 \pm 68 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 40 \pm 66 $ & $ 185 \pm 66 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 90 \pm 68 $ & $ 105 \pm 69 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 103 \pm 70 $ & $ 88 \pm 71 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 96 \pm 73 $ & $ 125 \pm 74 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 45 \pm 78 $ & $ 181 \pm 79 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 661 \pm 324 $ & $ 373 \pm 324 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 466 \pm 200 $ & $ 757 \pm 200 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
\enddata
\vspace{-0.8cm}
\tablecomments{comments}
\end{deluxetable*}

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
\caption{Dayside emission spectrum.}
\label{fig:dayside}
\end{figure}

@@

These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient, and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCM (FIXME define?) simulations.

The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).

@@

We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases. The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9. The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside. We report the best fit temperatures with uncertainties in Table\,\ref{tab:depths}.  The dayside spectrum is the poorest fit by the blackbody model. This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}. The more sophisticated grid-based retrieval provides a better fit to the dayside.

%Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$). However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features. We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.

@@

\subsection{Comparison with GCMs}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).

>>>>

\begin{deluxetable}{llllll}
\label{tab:model_comparison}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
\end{deluxetable}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag} = 10^3$ s. Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
\label{fig:spectra}
\end{figure*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM. We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

\begin{deluxetable*}{lllllllllll}
	\tablecolumns{11}
	\tablewidth{0pt}:
	\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
	\tablehead{
	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
		\startdata
		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable*}

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange. We also show a blackbody model (fit to the WFC3 data only).}
\label{fig:dayside}
\end{figure}

@@

These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient, and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

%The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).

@@

We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases. The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9. The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside. We report the best fit temperatures with uncertainties in Table\,\ref{table:teffs}.  The dayside spectrum is the poorest fit by the blackbody model. This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}. The more sophisticated grid-based retrieval provides a better fit to the dayside.

\begin{deluxetable}{lll}
	\tablecolumns{3}
	\tablewidth{0pt}:
	\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}
	\tablehead{
	\colhead{Phase} & \colhead{Effective Temperature} & \colhead{$\chi^2_\nu$}}
		\startdata
		0.1 & $ 1919 \pm 40 $ & 0.6 \\
		0.2 & $ 2256 \pm 24 $ & 0.8 \\
		0.3 & $ 2651 \pm 17 $ & 1.2 \\
		0.4 & $ 2906 \pm 11 $ & 0.8 \\
		0.5 & $ 3013 \pm 8 $ & 1.6 \\
		0.6 & $ 2885 \pm 12 $ & 1.3 \\
		0.7 & $ 2636 \pm 16 $ & 0.9 \\
		0.8 & $ 2313 \pm 23 $ & 1.1 \\
		0.9 & $ 2027 \pm 36 $ & 0.5 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable}
%Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$). However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features. We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.

@@

\subsection{Comparison with GCMs}
\label{sec:gcm}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).
